---
title: "Salinity and Temperature Quarterly Reports"
output: word_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library("tidyverse")
library("lubridate")
library("waterData")
library("dplyr")
library("ggplot2")
```



```{r salinity_data_processing, include=FALSE}


source("script/dailyFunctions.R")

# Sensor water quality carpentry
wq <- read.csv("data/wq.csv", header= T) %>%
  filter(Site != 0)
wq$Date <- wq$Date %>% ymd_hms %>% round_date(unit="hour")
wq$Site <- factor(wq$Site, levels = c("6", "1", "7", "5", "2", "8","4", "3", "9"))

# Water discharge carpentry (dynamically updating local discharge file)
station = '02323500' 
stinfo  = siteInfo(station)
dis <- read_rds("data/dis.rds")
if (max(dis$dates) < (Sys.Date() - 5)) {
  sdate <- max(dis$dates) + 1
  newdis <- importDVs(staid = station, code = '00060', stat = '00003', 
                      sdate= as.character(sdate))
  dis <- bind_rows(dis, newdis) %>%
    distinct() # In case there's repeated rows due to code failure
  write_rds(dis, "data/dis.rds")
}

# Define start and end date of the plot
####ALWAYS CHANGE THIS DATE TO THE LAST UPLOAD TIME##################################################
startDate <- ymd_hms("2017-08-16 00:00:00")
endDate <- ymd_hms("2018-10-04 23:00:00")

# Create sequence of dates (so that NA is recognized by geom_line) and build a table of
d <- seq(startDate, endDate, by = "hour")

dsal <- seq(startDate, endDate, by = "hour")
sal_only <- expand(wq, Site, Date=dsal) %>%
  left_join(wq, by=c("Site" = "Site", "Date" = "Date")) %>%
  select(Site, Date, Salinity)
sal_only$dsal2 <- date(sal_only$Date)


sal_summ <- sal_only %>%
  filter(Site %in% c("6","5","4","7","8","9","1","2","3"))%>%
  gather(key = "Measure", value = "Value", Salinity) %>%
  group_by(Site, dsal2, Measure) %>%
  summarise(meanVal = dailyMean(Value, 0.75), 
            minVal = dailyMin(Value, 0.75), 
            maxVal = dailyMax(Value, 0.75)) %>%
  ungroup()


dis2 <- dis %>%
  mutate(Datetime = paste(dates, " 12:00:00") %>% ymd_hms()) %>%
  filter(Datetime >= startDate & Datetime <= endDate)

dis3 <- dis2 %>%
  expand(Site=unique(sal_summ$Site), dates) %>%
  left_join(dis2) %>%
  mutate(Measure = "Discharge", minVal = -20, maxVal = val/1000 - 20) %>%
  select(Site, d2 = dates, Measure, minVal, maxVal)

```


```{r salinity_allsites, width= 12, height=12}

ggplot() +
  geom_line(data=sal_summ, aes(x=dsal2, y=meanVal, fill = "Salinity"), size= 1.1, color= "#0072B2") +
  geom_ribbon(data=dis3, aes(x=d2, ymax=maxVal, ymin=minVal, fill=Measure), 
              alpha=0.4) +
  xlab("Date") +
  scale_y_continuous(name = "Salinity(ppt)", 
                     limits=c(-20,40), 
                     breaks = seq(0, 40, 10),
                     sec.axis = sec_axis(~(.+20), 
                                         name = "River Discharge (1,000 cfs)
                                         ",
                                         breaks = seq(0, 20, 10))) +
  scale_x_date(date_breaks = "2 months", date_labels = "%y-%m-%d", expand = c(0, 0)) +
  
  scale_fill_manual(values = c("#56B4E9", "#0072B2")) +
  
  scale_color_manual(values = c("#56B4E9", "#0072B2")) +
  
  theme(legend.position=("top"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=10),
        axis.title=element_text(size=13,face="bold"),
        plot.title =element_text(size=13, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1, face= "bold"),
        axis.text.y = element_text(face= "bold"),
        legend.title=element_blank()) +
  
  guides(color = guide_legend(override.aes = list(linetype = c(0, 1)))) +
  
  facet_wrap(~ Site, ncol=3, labeller = label_both)


```


Figure 1.  Salinity and discharge data collected from autonomous sensors from the Lone Cabbage Reef restoration site near Suwannee, FL.  Each graph represents a sensor location, with top of page as north, and right of page as east.  The center column of figures (Sites 1-3) represent the eastern side of the Lone Cabbage Reef restoration site. The left column of figures (Sites 4-6) represent the western side of the Lone Cabbage Reef restoration site.  The right column of figures (Sites 7-9) represent sensors close to shore in an area where salinity may be influenced by restoring Lone Cabbage Reef.  The first two columns from the west (Sites 1-6) represent the inshore and offshore sides of the restoration reef.  The primary y-axis is Salinity (ppt, parts per thousand), and the secondary y-axis is Suwannee River discharge (CFS, cubic feet per second) measured at USGS Wilcox station 02323500 on the Suwannee River.  River discharge is graphed as a daily mean in the light blue filled shape near the bottom of each graph. Daily mean Salinity values (dark blue line) are shown in the center of each graph. The shaded dark blue region of the Salinity values are minimum and maximum values of that date. Missing values are provisional data that have not been finalized or represent periods of time when sensors were not yet deployed or off line due to user error or vandalism.



```{r alltemp_plots_processing, include= FALSE}

source("script/dailyFunctions.R")

# Sensor water quality carpentry
wq <- read.csv("data/wq.csv", header= T) %>%
  filter(Site != 0)
wq$Date <- wq$Date %>% ymd_hms %>% round_date(unit="hour")
wq$Site <- factor(wq$Site, levels = c("6", "1", "7", "5", "2", "8","4", "3", "9"))

# Water discharge carpentry (dynamically updating local discharge file)
station = '02323500' 
stinfo  = siteInfo(station)
dis <- read_rds("data/dis.rds")
if (max(dis$dates) < (Sys.Date() - 5)) {
  sdate <- max(dis$dates) + 1
  newdis <- importDVs(staid = station, code = '00060', stat = '00003', 
                      sdate= as.character(sdate))
  dis <- bind_rows(dis, newdis) %>%
    distinct() # In case there's repeated rows due to code failure
  write_rds(dis, "data/dis.rds")
}

# Define start and end date of the plot
####ALWAYS CHANGE THIS DATE TO THE LAST UPLOAD TIME#########################
startDate <- ymd_hms("2017-08-16 00:00:00")
endDate <- ymd_hms("2018-10-04 23:00:00")

# Create sequence of dates (so that NA is recognized by geom_line) and build a table of
d <- seq(startDate, endDate, by = "hour")
sal_temp <- expand(wq, Site, Date=d) %>%
  left_join(wq, by=c("Site" = "Site", "Date" = "Date")) %>%
  select(Site, Date, Salinity, Temperature)
sal_temp$d2 <- date(sal_temp$Date)

dtemp <- seq(startDate, endDate, by = "hour")
temp_only <- expand(wq, Site, Date=dtemp) %>%
  left_join(wq, by=c("Site" = "Site", "Date" = "Date")) %>%
  select(Site, Date, Temperature)
temp_only$dtemp2 <- date(temp_only$Date)

# Calculate mean, min and max daily Sal and Temp
# Note: tidyr's gather is in use here, by converting the "wide" table to
# "long" one, we can use the aes(color=Measure) in ggplot
# Note2: I've created functions in dailyFunction.R to make calculating daily mean, min,
# max easy. The function allows certain proportions of NA here. In this example, 0.75
# of the daily numbers can be NA, and we'll still calculate the meant, min, max

temp_summ <- temp_only %>%
  filter(Site %in% c("6","5","4","7","8","9","1","2","3"))%>%
  gather(key = "Measure", value = "Value", Temperature) %>%
  group_by(Site, dtemp2, Measure) %>%
  summarise(meanVal = dailyMean(Value, 0.75), 
            minVal = dailyMin(Value, 0.75), 
            maxVal = dailyMax(Value, 0.75)) %>%
  ungroup()

dis2 <- dis %>%
  mutate(Datetime = paste(dates, " 12:00:00") %>% ymd_hms()) %>%
  filter(Datetime >= startDate & Datetime <= endDate)

dis3 <- dis2 %>%
  expand(Site=unique(temp_summ$Site), dates) %>%
  left_join(dis2) %>%
  mutate(Measure = "Discharge", minVal = -20, maxVal = val/1000 - 20) %>%
  select(Site, d2 = dates, Measure, minVal, maxVal)


```


```{r}
ggplot() +
  geom_ribbon(data=dis2, aes(x=dates, ymax=val/1000 - 20, ymin=-20), 
              alpha=0.5, fill= "#56B4E9") +
  geom_line(data=std_summ, aes(x=d2, y=meanVal, color=Measure), size=1.2) +
  geom_ribbon(data=std_summ, aes(x=d2, ymax=maxVal, ymin=minVal, fill=Measure), 
              alpha=0.5) +
  xlab("Date") +
  scale_y_continuous(name = "Salinity(ppt) & Temperature (C)", 
                     limits=c(-20,40), 
                     breaks = seq(0, 40, 10),
                     sec.axis = sec_axis(~(.+20), 
                                         name = "River Discharge (1,000 cfs)
                                         ",
                                         breaks = seq(0, 20, 10))) +
  scale_x_date(date_breaks = "2 months", date_labels = "%y-%m-%d", expand = c(0, 0)) +
  
  scale_fill_manual(values = c("#56B4E9", "#0072B2", "#D55E00")) +
  
  scale_color_manual(values = c("#56B4E9", "#0072B2", "#D55E00")) +
  
  theme(legend.position=("top"),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_rect(color = "black", size = 1, fill = NA, linetype="solid"),
        axis.text=element_text(size=10),
        axis.title=element_text(size=13,face="bold"),
        plot.title =element_text(size=13, face='bold'),
        axis.text.x = element_text(angle = 90, hjust = 1, face= "bold"),
        axis.text.y = element_text(face= "bold"),
        legend.title=element_blank()) +
  
  guides(color = guide_legend(override.aes = list(linetype = c(0, 1,1)))) +
  
  facet_wrap(~ Site, ncol=3, labeller = label_both)
```





Figure 2.  Temperature and discharge data collected from autonomous sensors from the Lone Cabbage Reef restoration site near Suwannee, FL.  Each graph represents a sensor location, with top of page as north, and right of page as east.  The center column of figures (Sites 1-3) represent the eastern side of the Lone Cabbage Reef restoration site. The left column of figures (Sites 4-6) represent the western side of the Lone Cabbage Reef restoration site.  The right column of figures (Sites 7-9) represent sensors close to shore in an area where salinity may be influenced by restoring Lone Cabbage Reef.  The first two columns from the west (Sites 1-6) represent the inshore and offshore sides of the restoration reef.  The primary y-axis is Temperature (C, Celsius), and the secondary y-axis is Suwannee River discharge (CFS, cubic feet per second) measured at USGS Wilcox station 02323500 on the Suwannee River.  River discharge is graphed as a daily mean in the light blue filled shape near the bottom of each graph. Daily mean Temperature values (orange line) are shown in the center of each graph. The shaded orange region of the Temperature values are minimum and maximum values of that date. Missing values are provisional data that have not been finalized or represent periods of time when sensors were not yet deployed or off line due to user error or vandalism.







